---
title: "Dylan Padilla's CV"
author: Dylan Padilla
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "/Users/dpadil10/ASU Dropbox/Dylan Padilla/CV/pagedown-cv/",  
  pdf_mode = params$pdf_mode
)

```

```{css, echo=FALSE}

.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```


Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```



Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown). 

The source code is available [on github.com/Dylan-Padilla/pagedown-cv](https://github.com/Dylan-Padilla/pagedown-cv).

Last updated on `r Sys.Date()`.



Main
================================================================================

Dylan Padilla {#title}
--------------------------------------------------------------------------------

<p align="justify">
I am an Evolutionary Biology PhD candidate at the School of Life Sciences, [Arizona State University](https://www.asu.edu/). My research examines macro- and microevolutionary patterns in the life history of vertebrates and invertebrates (e.g., [see here](https://www.dropbox.com/s/9umvsjpvn7mj2eb/Padilla%20Perez%20D.J.%20and%20Angilletta%20Jr.%2C%20M.J.%20%282022%29.%20Macroclimatic%20and%20maternal%20effects%20on%20the%20evolution%20of%20reproductive%20traits%20in%20lizards.pdf?dl=0)).
</p>
<p align="justify">
As I am passionate about teaching, I often unlock new learning realms for my students by merging innovative efforts with advanced, adaptive educational experiences that eliminate educational inequities. I strongly believe that Diversity, Equity, and Inclusion in my teaching creates a learning environment that values all students' differences and ensures they feel included and supported. Check my most recent teaching project [**here**](https://www.youtube.com/@asnamnat9152/shorts).
</p>


```{r}
# Note the special double pipe so we modify the CV object in place
#CV %<>% print_text_block("intro") 
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```



Jobs and Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_positions')
```

Peer-reviewed Publications {data-icon=book}
--------------------------------------------------------------------------------

```{r}

CV %<>% print_section('academic_articles')

```


Teaching experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}

CV %<>% print_section('teaching')

```

GRANTS AND AWARDS {data-icon=award}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('data_grant')
```

Member of committee and Mentoring {data-icon=book-reader}
--------------------------------------------------------------------------------


```{r}

CV %<>% print_section('data_com')

```


RECENT TALKS, INVITED TALKS, WORKSHOPS ATTENDED {data-icon=users}
--------------------------------------------------------------------------------


```{r}

CV %<>% print_section('data_talks')
```

Service and Society member {data-icon=handshake}
--------------------------------------------------------------------------------


```{r}

CV %<>% print_section('data_mem')
```

Reviewer {data-icon=pencil}
--------------------------------------------------------------------------------


```{r}

CV %<>% print_section('data_rev')
```

Languages {data-icon=commenting}
--------------------------------------------------------------------------------


```{r}

CV %<>% print_section('data_lang')
```
