\listfiles
\documentclass[12pt]{article}
% -------------------------------------------------------------------
% Basic packages
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{fancyhdr}
\usepackage{setspace}

% -------------------------------------------------------------------
% Math packages
\usepackage{amsmath,amsfonts,amssymb,amsthm,cancel,siunitx,calculator,calc,mathtools,empheq,latexsym,inputenc}
% -------------------------------------------------------------------
% Packages for figures
\usepackage{subfig,epsfig,tikz,float}
% -------------------------------------------------------------------
% Packages for tables
\usepackage{booktabs,multicol,multirow,tabularx,array}

% -------------------------------------------------------------------

% Margins

\usepackage[a4paper,
            bindingoffset=0.2in,
            left=1in,
            right=1in,
            top=1.2in,
            bottom=1.2in,
            footskip=.25in]{geometry}

\linespread{2}
\linenumbers


% -------------------------------------------------------------------
% Title
\title{\renewcommand{\baselinestretch}{1.17}\large\bf Geographic and seasonal variation of the \textit{for} gene reveal signatures of local adaptation in \textit{Drosophila melanogaster}
}

% -------------------------------------------------------------------
% Authors

% Authors
\author{\normalsize
Dylan J. Padilla Perez
}


% -------------------------------------------------------------------

% Begin document

\begin{document}


\date{}

\maketitle

\vspace{-0.5cm}

School of Life Sciences, Arizona State University, Tempe, Arizona 85287, USA. \vspace{6pt} \\ \textbf{Corresponding author:} dpadil10@asu.edu.

\vspace{6pt}

\section*{\normalsize Acknowledgements}I thank Drs Michael Angilletta, Jay Taylor, Joaquin Nunez, and John VandenBrooks for providing helpful comments on earlier versions of this manuscript. I also thank the Drosophila Genome Nexus project, the European Drosophila Population Genomics Consortium, and the Real Time Evolution Consortium for providing easy access to the data used in this study.

\section*{\normalsize Data Accessibility Statement}%\label{sec:3}

A fully reproducible workflow of the data analyses, including R scripts and additional supporting material, is available in the following repositories: Github \url{https://dylan-padilla.github.io/for-evo/}.
\section*{\normalsize Conflict of interest}%\label{sec:3}

The author has declared no competing interests.

\section*{\normalsize Author Contributions}Dylan Padilla: Conceptualization, data curation, and formal analysis. Writing – original  draft, writing –  review and editing. The author agreed to be held accountable for the work performed herein.


\end{document}
